### 2016-07-15 Renormalization.tex
COMMITTED VERSION

\subsubsection*{The Quark Self-Energy}
The quark self-energy (depicted in fig. \ref{fig:QuarkSelfEnergy}) splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The one-particle-irreducible diagrams evaluate to
\begin{align}
i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,-0.1) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0,
\end{align}
where $\Re (\hdots)$ denotes the real part of $\hdots$, one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
\end{align}
Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$. These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} equal to be zero. Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part. Note further that the term $\frac{1}{2}$ from eq. \eqref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

@@

As for the quarks, the fermion (and momentum) flow in a diagram is from the right to the left. The one-particle irreducible Green function is given by

@@

Apart from the renormalization constant of the gauge coupling and the supersymmetry restoring counterterm these are all renormalization constants needed from squark production at next to leading order. In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams. This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams shown in fig. \ref{fig:CounterTerm}:

@@

@@

\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0.2) {1L};
	\node at (0,-0.18) {light};
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[gluon](-1.3,0)--(0,0);
	\draw[gluon](0,0)--(1.3,0);
	\draw[gluon] (0,0) arc (-90:270:.5);
	\node at (0,1.3) {$G$};
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7.0,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[fermion] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {light $q$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {light $q$};	
	\draw[gluon](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(10.5,0)}]
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[ghost] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\eta$};
	\draw[ghost] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\eta$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\begin{scope}[shift={(3.5,-2.5)}]
	\node at (-1.8,0) {+};
	\draw[gluon](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[gluon] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$G$};	
	\draw[gluon](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Contribution to the self-energy of the gluon originating from light particles.}\label{fig:lightGluonSelfEnergy}
\end{center}
\end{figure}

@@

@@

	\draw[fermionbar](-45:0.5)--(-45:1.3);

@@

	\draw[fermionbar](180:0.5)--(-45:0.5);

@@

	\draw[scalarbar](180:0.5)--(-45:0.5);

@@

\subsubsection{Implementation into the Model File}\label{sec:ModelFileImplementation}
Within the automated calculation, the renormalization of the matrix element of squark production has been achieved by extending the model file generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\ 
The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the model file was mainly done by Philip Dießner, another member of the group. To explain the implementation, the code extract describing the quark-squark-gluino vertex is considered, as an example.
\begin{lstlisting}[style=MyMathematica]
C[F[3, {gt1, ct1}], F[15, {ct2}], -S[13, {gt3, ct3}]] == {{
((-I)*g3*Lam[ct2, ct3, ct1]*(Conjugate[ZUL[gt1, 1]]*ZU[gt3, 1] + Conjugate[ZUL[gt1, 2]]*ZU[gt3, 2] + Conjugate[ZUL[gt1, 3]]*ZU[gt3, 3]))/Sqrt[2],
((-I)*(dZFu1[gt1]/2+dZSu1[gt3]/2+dZGlL1/2+dZgs1+dZgs1restore)*g3*Lam[ct2, ct3, ct1]*(Conjugate[ZUL[gt1, 1]]*ZU[gt3, 1] + Conjugate[ZUL[gt1, 2]]*ZU[gt3, 2] + Conjugate[ZUL[gt1, 3]]*ZU[gt3, 3]))/Sqrt[2]
}, {0,0}}
\end{lstlisting}
The syntax of the vertex, also described in \cite{FeynArtsManual}, is like $\left\{\left\{\mathrm{L},\mathrm{L}^{ct}\right\},\left\{\mathrm{R},\mathrm{R}^{ct}\right\}\right\}$, where the shortcuts are explained in table \ref{tab:Modelfille}.
The names of the particles within the model are given in the \texttt{FeynArts} manual\cite{FeynArtsManual} when  \texttt{MSSMQCD.mod}, the QCD extention of the MSSM model file, is explained.\\ 
However, \mbox{\texttt{F[3,$\left\{ \right.$gt1, ct1$\left.\right\}$]}} is an up-type quark of the \texttt{gt1}'th generation with color \texttt{ct1} and \texttt{F[15,$\left\{ \right.$ct2$\left.\right\}$]} is a gluino with color \texttt{ct2}. In comparison to \cite{FeynArtsManual}, there is a slight difference in the definition of squarks. Whereas the MSSM model file, \texttt{MSSMQCD.mod}, has three indices to label squarks, the model file generated by \texttt{SARAH} uses only two: \texttt{-S[13,$\left\{ \right.$ gt3, ct3$\left.\right\}$]} denotes an anti up-type squark of mass eigenstate \texttt{gt3} and color \texttt{ct3}. This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed'' squarks with increasing mass.
\begin{table}[H]
\begin{center}
\begin{tabular}{c?c}
Shortcut & Meaning\\
\hlinewd{2pt}
L & coupling proportional to the projector $P_L$ \\
L$^\mathrm{ct}$ & counterterm for L \\
R & coupling proportional to the projector $P_R$ \\
R$^\mathrm{ct}$ & counterterm for R \\
\end{tabular}
\caption{Explanation of the shortcuts describing the vertex structure in the above given mode extract.}\label{tab:Modelfille}
\end{center}
\end{table}

@@

\begin{lstlisting}[style=MyMathematicaOutput]

>>>>

\subsubsection*{The Quark Self-Energy}
The quark self-energy (depicted in fig. \ref{fig:QuarkSelfEnergy}) splits into contribution from the Standard Model as well as a supersymmetric analogue which is already present in the MSSM.
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (0.5,0) arc (0:-180:.5);	
	\node at (0,0) {1L};
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {=};
\begin{scope}[shift={(3.5,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$G$};
	\draw[fermion] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$q$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
	\node at (1.8,0) {+};
\end{scope}
\begin{scope}[shift={(7,0)}]
	\draw[fermionbar](180:1.3)--(180:0.5);
	\draw[gluon] (-0.5,0) arc (180:0:.5);
	\draw[fermionnoarrow] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\tilde{g}$};
	\draw[scalar] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\tilde{q}$};	
	\draw[fermionbar](0:0.5)--(0:1.3);
\end{scope}
\end{tikzpicture}
\caption{Feynman diagrams contributing to the self-energy of the quark at 1-loop level.}\label{fig:QuarkSelfEnergy}
\end{center}
\end{figure}\\
The one-particle-irreducible diagrams evaluate to
\begin{align}
i\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j} = i \frac{g_s^2}{16\pi^2}\delta_{ij} C(F) \left[ 2 \left( B_0(p^2,0,0) + B_1(p^2,0,0)-\frac{1}{2}\right)\slashed{p} - 2 B_1(p^2,m_{\tilde{g}}^2,m_{\tilde{q}}^2)\slashed{p}\right].\label{eq:QuarkSE}
\end{align}
With the counterterm Feynman rule\\
\\
\begin{tikzpicture}[line width=1.0 pt, scale=0.8]
	\node at (-2.5,-0.1) {$i\Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}\ \hat{=}\ i$};
\begin{scope}[shift={(0.1,0)}]	
	\draw[fermionbar] (-1.3,0) --(0,0);
	\draw[fermionnoarrow] (-0.3,0.3) -- (0.3,-0.3);
	\draw[fermionnoarrow] (-0.3,-0.3) -- (0.3,0.3);
	\draw[fermionbar] (0,0) --(1.3,0);
	\node at (1.6,-0.1) {$j$};
	\node at (3,0) {$\hat{=}\ i\delta_{ij}\delta Z_q \slashed{p} $};	
\end{scope}
\end{tikzpicture}\\
and the on-shell renormalization condition
\begin{align}
\frac{\partial}{\partial \slashed{p}} \left[ \Re (\Gamma^{\mathrm{1L}}_{q_i\overline{q}_j}) + \Gamma^{\mathrm{1L,ct}}_{q_i\overline{q}_j}  \right]_{p^2 = 0} = 0,
\end{align}
where $\Re (\hdots)$ denotes the real part of $(\hdots)$, one finds
\begin{align}
\delta Z_q = 2 C(F) \frac{g_s^2}{16\pi^2} \Re \left[ B_1(0 ,m_{\tilde{g}}^2,m_{\tilde{q}}^2) \right].
\end{align}
Note that the Standard Model contribution to the quark renormalization constant equals zero as it is propotional to $B_0(0,0,0)$ and $B_1(0,0,0)$. These integrals have no mass scale and are due to their definition of their scaling in $D$ dimensions\cite{Collins:105730} equal to be zero. Pictorially this may be understood as a cancellation of a positive UV-divergent part and a negative IR-divergent part. Note further that the term $\frac{1}{2}$ from eq. \eqref{eq:QuarkSE} has vanished because it has been absorbed in $B_0(p^2,0,0)|_{p^2 \to 0}$.\\
Doing the same calculation in DRED one finds that this very term $\frac{1}{2}$ is absent. Therefore the transition renormalization constant between DREG and DRED is given by
\begin{align}
\delta Z_q^{\mathrm{trans}} = \delta Z_q^{\mathrm{DREG}} - \delta Z_q^{\mathrm{DRED}} = C(F) \frac{g_s^2}{16\pi^2}.\label{eq:QuarkSC}
\end{align}

@@

As for the quarks, the fermion (and momentum) flow in a diagram is from the right to the left. The Feynman diagrams for the gluino self-energy are shown in \ref{fig:GluinoSE}. The one-particle irreducible Green function is given by

@@

Apart from the renormalization constant of the gauge coupling and the supersymmetry restoring counterterm these are all renormalization constants needed from squark production at next to leading order. In fact the field renormalization constants of the gluino are not needed as they drop out when summing up all three counterterm Feynman diagrams. 
\begin{figure}[H]

@@

This can be seen when writing down the matrix amplitudes for the counterterm Feynman diagrams shown in fig. \ref{fig:CounterTerm}:

@@

@@

	\draw[gluon] (0,0) arc (-90:270:.5);
	\node at (0,0.8) {light $q$};
	\node at (0,-0.8) {light $q$};	
	\draw[ghost] (-0.5,0) arc (180:0:.5);
	\node at (0,0.8) {$\eta$};
	\draw[ghost] (0.5,0) arc (0:-180:.5);
	\node at (0,-0.8) {$\eta$};	
	\node at (0,-0.8) {$G$};	
\caption{Contribution to the self-energy of the gluon originating from light particles.}\label{fig:lightGluonSelfEnergy}

@@

	\draw[fermion](-45:0.5)--(-45:1.3);

@@

	\draw[fermion](180:0.5)--(-45:0.5);

@@

	\draw[scalar](180:0.5)--(-45:0.5);

@@

\subsubsection{Implementation into the Model File}\label{sec:ModelFileImplementation}
Within the automated calculation, the renormalization of the matrix element of squark production has been achieved by extending the model file generated by \texttt{SARAH} with counterterm Feynman rules and renormalization constants.\\ 
The derivation of the counterterm Feynman rules has been performed by the author whereas the implementation into the model file was mainly done by Philip Dießner, another member of the group. To explain the implementation, the code extract describing the quark-squark-gluino vertex is considered as an example.
\begin{lstlisting}[style=MyMathematica]
C[F[3, {gt1, ct1}], F[15, {ct2}], -S[13, {gt3, ct3}]] == {{
((-I)*g3*Lam[ct2, ct3, ct1]*(Conjugate[ZUL[gt1, 1]]*ZU[gt3, 1] + Conjugate[ZUL[gt1, 2]]*ZU[gt3, 2] + Conjugate[ZUL[gt1, 3]]*ZU[gt3, 3]))/Sqrt[2],
((-I)*(dZFu1[gt1]/2+dZSu1[gt3]/2+dZGlL1/2+dZgs1+dZgs1restore)*g3*Lam[ct2, ct3, ct1]*(Conjugate[ZUL[gt1, 1]]*ZU[gt3, 1] + Conjugate[ZUL[gt1, 2]]*ZU[gt3, 2] + Conjugate[ZUL[gt1, 3]]*ZU[gt3, 3]))/Sqrt[2]
}, {0,0}}
\end{lstlisting}
The syntax of the vertex, also described in \cite{FeynArtsManual}, is like $\left\{\left\{\mathrm{L},\mathrm{L}^{ct}\right\},\left\{\mathrm{R},\mathrm{R}^{ct}\right\}\right\}$, where the shortcuts are explained in table \ref{tab:Modelfille}.
The names of the particles within the model are given in the \texttt{FeynArts} manual\cite{FeynArtsManual} when  \texttt{MSSMQCD.mod}, the QCD extention of the MSSM model file, is explained.\\ 
However, \mbox{\texttt{F[3,$\left\{ \right.$gt1, ct1$\left.\right\}$]}} is an up-type quark of the \texttt{gt1}'th generation with color \texttt{ct1} and \texttt{F[15,$\left\{ \right.$ct2$\left.\right\}$]} is a gluino with color \texttt{ct2}. In comparison to \cite{FeynArtsManual}, there is a slight difference in the definition of squarks. Whereas the MSSM model file, \texttt{MSSMQCD.mod}, has three indices to label squarks, the model file generated by \texttt{SARAH} uses only two: \texttt{-S[13,$\left\{ \right.$ gt3, ct3$\left.\right\}$]} denotes an anti up-type squark of mass eigenstate \texttt{gt3} and color \texttt{ct3}. This means more specifically that \texttt{gt3}$\in \left\{ 1,2,3 \right\}$ labels the ``left-handed" squarks with increasing mass and \texttt{gt3}$\in \left\{ 4,5,6 \right\}$ the ``right-handed'' squarks with increasing mass.
\begin{table}[H]
\begin{center}
\begin{tabular}{c?c}
Shortcut & Meaning\\
\hlinewd{2pt}
L & coupling proportional to the projector $P_L$ \\
L$^\mathrm{ct}$ & counterterm for L \\
R & coupling proportional to the projector $P_R$ \\
R$^\mathrm{ct}$ & counterterm for R \\
\end{tabular}
\caption{Explanation of the shortcuts describing the vertex structure in the above given mode extract.}\label{tab:Modelfille}
\end{center}
\end{table}

@@

\begin{lstlisting}[style=MyMathematica]

### 2016-07-15 Standardmodel.tex
COMMITTED VERSION

\section{The Standard Model}
The Standard Model of particle physics is the commonly accepted theory describing the world's fundamental particles and their interactions. It is a gauge quantum field theory and therefore characterized by its invariance under symmetry groups. The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
This chapter summarizes the most important aspects of the Standard Model.
%The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
%More formally a particle state is said to give rise to an irreducible representation of the Poincaré group

>>>>

\section{The Standard Model}
The Standard Model of particle physics is the commonly accepted theory describing all known fundamental particles and their non-gravitational interactions. It is a gauge quantum field theory and therefore characterized by its invariance under symmetry groups. The Standard Model contains different fields, whose quantized excitations are interpreted as particles.\\
This chapter summarizes the most important aspects of the Standard Model.
%The different fields defined on Minkowski space are Dirac spinors describing matter fields (leptons and quarks), gauge vectors describing force mediators and a scalar field (the Higgs) which accounts for the masses of particles.\\
%More formally a particle state is said to give rise to an irreducible representation of the Poincaré group

### 2016-07-15 Summary.tex
COMMITTED VERSION

The Standard Model of particle physics describes the world's fundamental particles and the interactions among them. It belongs to the best tested theory within physics but is on the other hand known to be incomplete.\\
Supersymmetry provides an attractive extension of the Standard Model. Within this thesis, a specific supersymmetric extension of the Standard Model - the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) - is studied. This is particularly appealing from the point of view of symmetries because it comprises the maximal possible symmetry group a reasonable quantum field theory can have. The theorem stating this is the Haag-Laopuszanski-Sohnius theorem. In contrast to the common notion, supersymmetry alone does not extent the Poincaré symmetry to the largest possible symmetry group. There is a further non-trivial extension by a global continuous symmetry, referred to as $R$-symmetry.\\
This thesis introduces an $R$-symmetric model in its minimal form. $R$-symmetry forbids terms which are allowed in the Minimal Supersymmetric Standard Model (MSSM). This includes the $A$-terms and the $\mu$-term which are responsible for squark mixing and flavor changing processes. But $R$-symmetry also prohibits Majorana mass terms for the gauginos. To be phenomenological viable, the MRSSM needs to accomodate Dirac gauginos. This requires the gauge sector of this model to be a $N=2$ supersymmetric theory which in turn implies further degrees of freedom.\\
Focusing on the strongly coupling sector, there is, apart from the ``usual'' gluino, another fermionic degree of freedom which is referred to the octino. The superpartner of this right handed part of the strongly coupling gaugino is a spin-0 particle: the scalar gluon (sgluon). As a matter of fact, there are two distinct real sgluons with distinct masses.\\ 
Within the framework of this thesis, the production cross section of squarks and gluinos in the MRSSM has been calculated at tree-level. To this end, Feynman rules for the strongly coupling sector of the MRSSM have been derived. The cross sections and intermediate results are given explicitly for each process. In comparison to the corresponding processes in the MSSM, it has been found that gluino production is enhanced by a factor of about two because gluino and antigluino are distinguishable particles, as opposed to in the MSSM. In order to meet the absence of signals alluding to supersymmetry at the LHC, this suggests that gluinos might be heavier than squarks if they should be realized in that way in nature. Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly lower than in the MSSM. The most striking difference has been found in the production channel of squarks. Motivated by this fact, the next-to-leading order cross section for squark production has been calculated.\\

@@

To this end, a model file generated by \texttt{Sarah}, which serves only for leading order processes, has been adjusted manually to incorporate counter term Feynman rules. At this point, Philip Dießner did a major contribution when the model file was changed. After this, the model file has been provided with appropriate renormalization constants which are explicitly given in the thesis. This also includes  a supersymmetry restoring counterterm. By means of this model file, renormalized one-loop corrections to the matrix element of squark production have been calculated in \texttt{Mathematica}, using the packages \texttt{FeynArts} and \texttt{FormCalc}. After this, the virtual contributions, which have been checked for ultraviolet-finiteness, have been passed to a \texttt{C++} code and have been evaluated using the \texttt{Looptools} package. Finally, the phase space integration has been performed numerically using the \texttt{CUBA} library for parallelized numerical integration. However, the virtual corrections to the cross section are not infrared finite. To render the next-to-leading order cross section $\sigma^{\mathrm{NLO}}$ finite, real corrections need to be included. This has been done by Wojciech Kotlarski. After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.

@@

$1000$ & $2000$ & $11.56$ & $14.3$ & $1.24$ & $6.36$ & $72.1$ & $1.09$\\

@@

\caption{Total hadronic cross section for the production of up-squarks through protons in the MRSSM and the MSSM at leading order and next-to-leading order. Also given are the $K$-factors. As a consequence of $R$-charge conservation, the only allowed channel in the MRSSM is $\tilde{u}_L + \tilde{u}_R$ production, whereas in the MSSM also $\tilde{u}_L + \tilde{u}_L$ and $\tilde{u}_R + \tilde{u}_R$ production is allowed.\newline 

@@

Equipped with this program, the $K$-factors for up-squark production have been calculated as a function of the squark mass and a function of the gluino mass. As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that the very same are slightly larger in the MRSSM. But since the tree-level cross section of squark production in the MRSSM is, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
Among other advantages to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.

>>>>

The Standard Model of particle physics describes all known fundamental particles and the non-gravitational interactions among them. It belongs to the best tested theories within physics but is on the other hand known to be incomplete.\\
Supersymmetry provides an attractive extension of the Standard Model. Within this thesis, a specific supersymmetric extension of the Standard Model -- the Minimal $R$-Symmetric Supersymmetric Standard Model (MRSSM) -- is studied. This is particularly appealing from the point of view of symmetries because it comprises the maximal possible symmetry group a reasonable quantum field theory can have. The theorem stating this is the Haag-{\L}opusza\'nski-Sohnius theorem. In contrast to the common notion, supersymmetry alone does not extent the Poincaré symmetry to the largest possible symmetry group. There is a further non-trivial extension by a global continuous symmetry, referred to as $R$-symmetry.\\
This thesis introduces an $R$-symmetric model in its minimal form. $R$-symmetry forbids some of the terms which are allowed in the Minimal Supersymmetric Standard Model (MSSM). These include the $A$-terms and the $\mu$-term which are responsible for squark mixing and flavor changing processes. Furthermore, $R$-symmetry also prohibits Majorana mass terms for the gauginos. To be phenomenologically viable, the MRSSM needs to accommodate Dirac gauginos. This requires the gauge sector of this model to be an $N=2$ supersymmetric theory which in turn implies further degrees of freedom.\\
Focusing on the strongly coupling sector, there is, apart from the ``usual'' gluino, another fermionic degree of freedom which is referred to as octino. The superpartner of this right handed part of the strongly coupling gaugino is a spin-0 particle: the scalar gluon (sgluon). As a matter of fact, there are two distinct real sgluons with distinct masses.\\ 
Within the framework of this thesis, the production cross section of squarks and gluinos in the MRSSM has been calculated at tree-level. To this end, Feynman rules for the strongly coupling sector of the MRSSM have been derived. The cross sections and intermediate results are given explicitly for each process. In comparison to the corresponding processes in the MSSM, it has been found that gluino production is enhanced by a factor of about two because of gluino and antigluino being distinguishable particles, unlike in the MSSM. In order to meet the absence of signals alluding to supersymmetry at the Large Hadron Collider (LHC), this suggests that gluinos might be heavier than squarks if they should be realized as Dirac fermions in nature. Focusing on this regime of parameter space, it has been found that the production of squarks and gluinos in the MRSSM is significantly suppressed compared to the MSSM. The most striking difference has been found in the production channel of squarks. Motivated by this fact, the next-to-leading order cross section for squark production has been calculated.\\

@@

To this end, a model file generated by \texttt{Sarah}, which serves only for leading order processes, has been adjusted manually to incorporate counterterm Feynman rules. At this point, Philip Dießner contributed significantly by changing model file. After this, the model file has been provided with appropriate renormalization constants which are explicitly given in the thesis. This also includes  a supersymmetry restoring counterterm. By means of this model file, renormalized one-loop corrections to the matrix element of squark production have been calculated in \texttt{Mathematica}, using the packages \texttt{FeynArts} and \texttt{FormCalc}. After this, the virtual contributions, which had been checked for ultraviolet-finiteness, have been passed to a \texttt{C++} code and evaluated using the \texttt{Looptools} package. Finally, the phase space integration has been performed numerically using the \texttt{CUBA} library for parallelized numerical integration. However, the virtual corrections to the cross section are not infrared finite. To render the next-to-leading order cross section $\sigma^{\mathrm{NLO}}$ finite, real corrections needed to be included. This has been done by Wojciech Kotlarski. After including them, $\sigma^{\mathrm{NLO}}$ has been found to contain no further divergences.\\
Equipped with this program, the $K$-factors for up-squark production have been calculated as a function of the squark and of the gluino mass. Table \ref{tab:Kfactors} summarizes leading and next-to-leading order cross sections as well as the $K$-factors for up-squark production in the MRSSM and MSSM at the LHC for a selected set of masses.

@@

$1000$ & $2000$ & $11.56$ & $14.3$ & $1.24$ & $66.36$ & $72.1$ & $1.09$\\

@@

\caption{Total hadronic cross sections for the production of up-squarks through protons in the MRSSM and the MSSM at leading and next-to-leading order. Also given are the $K$-factors. As a consequence of $R$-charge conservation, the only allowed channel in the MRSSM is $\tilde{u}_L + \tilde{u}_R$ production, whereas in the MSSM also $\tilde{u}_L + \tilde{u}_L$ and $\tilde{u}_R + \tilde{u}_R$ production are allowed.\newline 

@@

As a result, the comparison of $K$-factors for squark production in the MRSSM and the MSSM showed that they are slightly larger in the MRSSM. But since the tree-level cross section of squark production in the MRSSM is, depending on the choice  of squark and gluino mass, about an order of magnitude smaller than in the MSSM, this renders the MRSSM to a perfectly viable extension of the Standard Model.\\
Among other advantages compared to the MSSM, it explains a suppressed cross section for the production of supersymmetric particles at the LHC.
